---
title: "Messin Around"
author: "Bryant"
date: "2022-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
data <- read_csv("spam_ham.csv") %>%
  mutate(Label = ifelse(Label == "spam", 0,1)) 
view(data)
```


```{r}
print(names(data))
new_data = data %>% pivot_longer(cols = num_subj_adjs:perc_total_intj, 
                      names_to = "variables",
                      values_to = "values") %>% 
  separate(variables, c("count_freq", "subject_content_total", "pos")) %>% 
  pivot_wider(names_from = c("count_freq", "subject_content_total"),
              values_from = "values")

```

```{r}
print(names(new_data))
plot = new_data %>% filter(num_subj>0, perc_subj>0, num_cont>0, perc_cont>0, num_total>0, perc_total>0) %>% 
  ggplot(aes(factor(Label), fill = pos)) +
  geom_bar(position=position_dodge()) 
  
ggsave("visualization_dodge.png", height = 7, width = 8, dpi = 300)

plot = new_data %>% filter(num_subj>0, perc_subj>0, num_cont>0, perc_cont>0, num_total>0, perc_total>0) %>% 
  ggplot(aes(Label, fill = pos)) +
  geom_bar(position=position_fill()) 
  
ggsave("visualization_fill.png", height = 7, width = 8, dpi = 300)


```

```{r}
df_tbl = new_data %>% filter(num_subj>0, perc_subj>0, num_cont>0, perc_cont>0, num_total>0, perc_total>0) %>% 
  xtabs(~pos + Label, data = .) %>% 
  print()

means = new_data %>%
  group_by(pos,Label) %>% 
  summarise(n = n(),
            total_mean = mean(num_total),
            total_mean_perc = mean(perc_total),
            sd = sd(num_total),
            subj_mean = mean(num_subj),
            subj_mean_perc = mean(perc_subj)) %>% 
            

  print()

ham_adj_subj_count = new_data %>% filter(Label==1,pos=='adjs') %>% 
  select(num_subj) %>% 
  view()

spam_adj_subj_count = new_data %>% filter(Label==1,pos=='adjs') %>% 
  select(num_subj) %>% 
  view()

write_csv(means,"means.csv")

spam_mean = means %>% filter(Label == 0) %>% 
  print()
ham_mean = means %>% filter(Label == 1) %>% 
  print()

df_table = xtabs(~total_mean + Label, data = means) %>% 
  print()
```

## Chi-Squared Test
```{r}
rstatix::chisq_test(df_tbl)
#rstatix::chisq_test(df_tbl, p=c(1-.34684719535, .34684719535))
```
Our chi-squared test is extremely small so we have significant reason to reject the null hypothesis that there is not a difference between the two distributions. Now we find Cramer's V.

## Cramer's V
```{r}
vcd::assocstats(df_tbl)
```
Cramer's V is .106 which is pretty close to 0 so there is a weak association between part of speech and whether I opened the email or not.

# Chi-Squared on each PoS
We want to see which part of speeches are actually significant. Because it is impossible to tell with 7 degrees of freedom. But now we know at least one of the variables is significant.

## Adjective
```{r}
df_tbl = new_data %>% filter(num_total>0, perc_total>0) %>% 
  filter(pos=="adjs") %>% 
  xtabs(~num_total + Label, data = .) %>% 
  print()

data %>% group_by(Label) %>% 
  count()

new_data %>% group_by(pos) %>% count()

spam_count = 12925
ham_count = 4483
```

## Chi-Squared Test
```{r}
rstatix::chisq_test(df_tbl)
```
Our chi-squared test is extremely small so we have significant reason to reject the null hypothesis that there is not a difference between the two distributions. Now we find Cramer's V.

## Cramer's V
```{r}
vcd::assocstats(df_tbl)
```

# New section
```{r}
summary = new_data %>% filter(num_total>0) %>% 
  group_by(pos) %>% 
  summarize(n=n(),
            mean=mean(num_total),
            sd = sd(num_total))
print(summary)
view(new_data)
```


```{r}
new_data %>% filter(num_total>0) %>% group_by(pos) %>% 
  ggplot(aes(num_total, color=Label, fill=Label))+
  geom_density(alpha=.5) +
  xlim(0,10)
```


```{r}
# Our naive original model for adjectives
m_adjs = new_data %>% filter(pos == 'adjs') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_adjs))

m_advs = new_data %>% filter(pos == 'advs') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_advs))

m_noun = new_data %>% filter(pos == 'noun') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_noun))

m_num = new_data %>% filter(pos == 'num') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_num))

m_propn = new_data %>% filter(pos == 'propn') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_propn))

m_sym = new_data %>% filter(pos == 'sym') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_sym))

m_verb = new_data %>% filter(pos == 'verb') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_verb))

m_intj = new_data %>% filter(pos == 'intj') %>% 
  lm(Label ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
print(summary(m_intj))
```



```{r}
cat("Mean of the residuals = ", mean(residuals(m_adjs)))
```


```{r}
tibble(res = residuals(m_adjs)) %>% 
  ggplot(aes(res))+
  geom_histogram()+
  ggtitle("Histogram of raw residuals")
```


```{r}
res <- residuals(m_adjs)

ggplot(tibble(residuals(m_adjs)), aes(sample = res))+
  stat_qq()+
  stat_qq_line()+
  ggtitle("Q-Q plot of raw residuals")
```

```{r}
# BOX COX not the right thing because lambda will be 0 and then I have divide by 0 error
lambda <- bc$x[which.max(bc$y)]
m_adjs2 <- new_data %>% filter(pos == 'adjs') %>% 
  mutate(bc_rt = (Label ^ lambda - 1) / lambda) %>% 
  lm(bc_rt ~ num_subj + perc_subj + num_cont + perc_cont + num_total + perc_total, data = .)
```



```{r}
p_adjs = new_data %>% filter(pos == 'adjs') %>% 
  ggplot(aes(x = factor(Label), y = num_total)) +
  geom_boxplot(notch=TRUE)+
  stat_summary(fun=mean)+
  theme_bw()
p_adjs

p_advs = new_data %>% filter(pos == 'advs') %>% 
  ggplot(aes(x = factor(Label), y = num_total)) +
  geom_boxplot(notch=TRUE)+
  stat_summary(fun=mean)+
  theme_bw()
p_advs

p3 <- data %>%
  ggplot(aes(x = factor(Label), y = num_total_adjs))+
  geom_boxplot(notch = TRUE)+
  stat_summary(fun = mean)+
  facet_wrap(~num_total_advs)+
  theme_bw()
print(p3)

```

```{r}
m1 <- lm(Label ~ num_total_adjs + num_total_advs, data = data)
summary(m1)
```

```{r}
AIC(m1)
```

```{r}
m2 <- lm(Label ~ num_total_adjs + num_total_advs + num_total_adjs:num_total_advs, data = data)
summary(m2)
```

```{r}
AIC(m2)
```

```{r}
write_csv(new_data, "spam_ham_pivoted.csv")
```


```{python}
import numpy as np
print(np.array([1,2,3]))
```




